Effects of CHILDREN's programs

### 2020-02-24 paper.Rnw
created references file
ghjk
example for xtable adapted DiD for weights

% \addbibresource{Main.bib}

@@

% look up official names of price indices in English 
At the beginning of the time series in 2011, they supported in x institutions. In 2018, this number had increased to y. In this section, we give an overview of the dynamics of CHILDREN's two flagship programs. We focus on the number of estimated ultimate beneficiaries, median total subsidy, median subsidy per institution, and median subsidy per beneficiary. We also look at selected outcomes, i.e. those related to health as well as self-worth and day-to-day skills. We have converted all nominal monetary variables into 2015 euros, using price indices from the Federal Statistical Office of Germany (Statistisches Bundesamt). We deflate (requested) grants as well as organizations' total expenses for the Meals program  with the price index related to food and non-alcoholic beverages (in German: Nahrungsmittel und alkoholfreie Getränke) and (requested) grants towards the Trips program with the price index for leisure, entertainment, and culture (in German: Freizeit, Unterhaltung und Kultur). These are only available after logging in on DESTATIS. The organizations also gave information about their total yearly budget. We inflate this with the general price index.

@@

%\printbibliography
\end{document}

>>>>

\addbibresource{references.bib}

@@

% <<results='asis', echo=FALSE>>=
% tableCyclicDisp = readRDS("./Analysis/CyclicDisp.Rds")
% colnames(tableCyclicDisp) <- c("Lead in years", "All", "p-value", "Non-Durables", "p-value", "Durables", "p-value")
% tableCyclicDisp <- xtable(tableCyclicDisp, caption = "Cyclicality of productivity dispersion", digits = c(0, 0, 3, 2, 3, 2, 3, 2))
% print(tableCyclicDisp, include.rownames = FALSE)
% @

<<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=

fundamental_dynamics = readRDS("./ANALYSIS/Tables/fundamental_dynamics.Rds")

colnames(fundamental_dynamics) <- c("Year", "Beneficiaries, Meals", "Beneficiaries, Trips", "Organizations, Meals", "Organizations, Trips")

fundamental_dynamics <- xtable(fundamental_dynamics,
                               digits = c(0, 0, 1, 1, 0, 0),
          caption = "Summary Statistics",
          align = "lmmmmm"
          )
print(fundamental_dynamics, include.rownames = FALSE)
@
% look up official names of price indices in English 
At the beginning of the time series in 2011, they supported in x institutions. In 2018, this number had increased to y. In this section, we give an overview of the dynamics of CHILDREN's two flagship programs. We focus on the number of estimated ultimate beneficiaries, median total subsidy, median subsidy per institution, and median subsidy per beneficiary. We also look at selected outcomes, i.e. those related to health as well as self-worth and day-to-day skills. We have converted all nominal monetary variables into 2015 euros, using price indices from the Federal Statistical Office of Germany (Statistisches Bundesamt). We deflate (requested) grants as well as organizations' total expenses for the Meals program  with the price index related to food and non-alcoholic beverages (in German: Nahrungsmittel und alkoholfreie Getränke) and (requested) grants towards the Trips program with the price index for leisure, entertainment, and culture (in German: Freizeit, Unterhaltung und Kultur). These are only available after logging in on DESTATIS. The organizations also gave information about their total yearly budget. We inflate this with the general price index.

@@

% table1_selfworth <- stargazer(lm1_selfworth,
%                     lm2_selfworth,
%                     lm3_selfworth,
%                     lm4_selfworth,
%           title = "Regression Results",
%           order = c('Constant', 'treatEF'),
%           omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
%                    'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
%                    'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
%                    'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
%                    'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
%                    'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
%                    'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
%                    'dummy_2018', 'id'
%                   ),
%           add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
%                            c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
%           align = TRUE)

% \begin{table}[!htbp] \centering 
%   \caption{Regression Results} 
%   \label{} 
% \begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
% \\[-1.8ex]\hline 
% \hline \\[-1.8ex] 
%  & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
% \cline{2-5} 
% \\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
% \\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
% \hline \\[-1.8ex] 
%  Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
%   & (0.065) & (0.095) & (0.092) & (0.107) \\ 
%   & & & & \\ 
%  treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
%   & (0.074) & (0.097) & (0.075) & (0.100) \\ 
%   & & & & \\ 
% \hline \\[-1.8ex] 
% ID fixed effects & No & No & Yes & Yes \\ 
% Time fixed effects & No & Yes & No & Yes \\ 
% Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
% R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
% Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
% Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
% F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\ 
% \hline 
% \hline \\[-1.8ex] 
% \textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
% \end{tabular} 
% \end{table}

\printbibliography
\end{document}
